\papertitle

### 2013-01-16 manuscript.tex
Add authors and acknowledgements

%% Paper number instead of authors
\numberofauthors{1}
\author{
\alignauthor Paper  580
}

%\numberofauthors{4}
%\author{
%\alignauthor Ryan C. Julian\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{ryanjulian@berkeley.edu}
%\alignauthor Cameron J. Rose\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{c\_rose@eecs.berkeley.edu}
%\alignauthor Humphrey Hu\\
%       \affaddr{Robotics Institute}\\
%       \affaddr{Carnegie Mellon University}\\
%       \affaddr{Pittsburgh, PA 15213}\\
%       \email{humhu@cmu.edu}
%\and
%\alignauthor Ronald S. Fearing\\
%       \affaddr{Department of EECS}\\
%       \affaddr{Univ. of California, Berkeley}\\
%       \affaddr{Berkeley, CA 94720}\\
%       \email{ronf@eecs.berkeley.edu}
%}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Acknowledgments}
%The authors would like to thank Fernando Garcia Bermudez for his 
%assistance with the Vicon motion capture system, Andrew Pullin for his 
%help with robot photography, and the members of the Biomimetic 
%Millisystems Laboratory and the EECS community at the University of 
%California, Berkeley for their advice and support.

>>>>

%% Paper number instead of authors
%\numberofauthors{1}
%\author{
%\alignauthor Paper  580
%}

\numberofauthors{4}
\author{
\alignauthor Ryan C. Julian\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{ryanjulian@berkeley.edu}
\alignauthor Cameron J. Rose\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{c\_rose@eecs.berkeley.edu}
\alignauthor Humphrey Hu\\
       \affaddr{Robotics Institute}\\
       \affaddr{Carnegie Mellon University}\\
       \affaddr{Pittsburgh, PA 15213}\\
       \email{humhu@cmu.edu}
\and
\alignauthor Ronald S. Fearing\\
       \affaddr{Department of EECS}\\
       \affaddr{Univ. of California, Berkeley}\\
       \affaddr{Berkeley, CA 94720}\\
       \email{ronf@eecs.berkeley.edu}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.
